An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-11-10 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Text of Energy Econ paper now reflects PWT source.

We measure economic output ($Y$) by gross domestic product (GDP). 
GDP data in real 2005 U.S. dollars for developed countries (1980--2011) 
and all other countries (1991--2011) was obtained from 
the World Bank's Global Economic Prospects (GEP) database 
\citep{WorldBankGEP:2013a}.

@@

Gross capital stock in real 2005 U.S. dollars 
for developed countries (1980--2011) and 
all other countries (1991--2011) was obtained from 
the World Bank's Global Economic Prospects (GEP) database 
\citep{WorldBankGEP:2013a}.

@@

Total employment and average hours worked per worker per year 
for the developed nations (United States, United Kingdom, and Japan) 
for 1980--2011 were obtained from the United States 
\citet[Tables 6 and 7]{BLS:2013a}. Total hours worked per year was 
calculated by multiplying total employment by average hours worked 
per worker per year.

The World Bank's World Development Indicators database 
\citep{WorldBankWDI:2013a} provides the employment to population 
ratio for people fifteen and older, total population, and a percentage 
of people under fifteen for other economies 
(China, South Africa, 
Saudi Arabia, Iran, 
Tanzania, and Zambia) 
for 1991--2011. 
The population 
of people under fifteen years of age was subtracted from total population 
to calculate the population of people fifteen and older. 
Total employment was calculated by multiplying the employment to 
population ratio of people fifteen and older by the population 
of people fifteen and older.

>>>>

We measure economic output ($Y$) by gross domestic product (GDP). 
GDP data in real 2005 U.S. dollars for all countries was obtained from the
RGDP$^{\mathrm{NA}}$ time series of the Penn World Table.~\citep{Feenstra:2013aa}

@@

Gross capital stock in real 2005 U.S. dollars 
for all countries was obtained from the
RK$^{\mathrm{NA}}$ time series of the Penn World Table.~\citep{Feenstra:2013aa}

@@

Total employment (persons engaged) for all countries
was obtained from the 
EMP time series of the Penn World Table.~\citep{Feenstra:2013aa}
The EMP time series was used as the labor factor of production 
for CN, ZA, SA, IR, TZ, and ZM.
For the developed nations (US, UK, and JP), 
average hours worked per worker per year 
was obtained from the AVH time series of the Penn World Table.~\citep{Feenstra:2013aa}
The product of EMP and AVH was used as the labor factor of production 
for the developed nations.
